Dark Control:\\ A Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-09-18 paper/paper.tex
fix Latex compile error
homogenize the 4 func acc

\begin{figure}[!h]
  \includegraphics[width=1\linewidth]{VennDiagram-2017-09-08.pdf}
  \caption{\textbf{Situating Markov Decision Processes among other accounts of default mode function}
  This Venn diagram summarizes the relationship between four existing explanations of the functional role of the DMN and our present account. Viewing empirical findings in the DMN from the MDP viewpoint incorporates important aspects of the free energy principle, predictive coding, sentinal hypothesis, and semantic hypothesis.
  % more related to "What" DMN does. Our account of DMN by Markov Decision Process is at the intersection of those accounts and thus corresponds to a "Process model" meaning a model of both "How" and "What" a process occur.
  The MDP account may reconcile several strengths of these functional accounts in a process model that simultaneously acknowledges environmental input and behavioral choices as well as the computational and algorithmic properties (How? and What?) underlying higher-order control of the organism.

  % ; here the mental processes and how it relate to observed behavior. For each account, 4 icons describe the core concepts of Time horizon, Neural plasticity, Hierarchy, and Behavioral goal. The "Time horizon" should be understood as a weighting of the expected future outcomes shorter to longer terms into present decision making. Then, "online monitoring" of the environment means detecting and processing salient cues in the sensory environment. The "Predictive Coding" is understood here as the joint minimization of feedforward prediction error and feedback modulation to optimize neural processing; there is thus no notion of an agent with behavioral goal.
  }
  \label{fig:VennDiagram}
\end{figure}

@@

% CRITICISM
\paragraph{Main criticisms.}
Despite its popularity, criticism against the FEP has arisen over the years,
some of which is outlined in the following.
The main algorithm for minimizing free energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}
\citep{dayan1995helmholtz}. As these P. Dayan and G. Hinton  noted,
a crucial drawback of the wake-sleep algorithm (and therefore of theories like the FEP \citep{friston2010free} based on it) is that it involves a pair
of forward (generation) and backward (recognition) models $p_G$ and $p_R$ respectively that
together do not correspond to optimization of (a bound of) the marginal likelihood,
because KL divergence is not symmetric in its arguments.
The brain may therefore be unlikely to implement a variant of the wake-sleep algorithm.
The recent theory of
\textit{variational auto-encoders} (VAEs) \citep{kingma2013auto} might provide an efficient alternative to the wake-sleep algorithm. VAEs
overcome a number of the technical limits of the wake-sleep algorithm
by using a reparametrization maneuver, which makes it possible to do differential calculus on random sampling procedures without exploding variance. As a result, unlike the wake-sleep algorithm
for minimizing free energy, VAEs can be efficiently trained via back-propagation of prediction errors.

@@

\paragraph{Links between FEP and RL.}
We note that FEP and active inference can be reframed in terms of
our model-free RL framework.
This becomes possible by recasting the Q-value function (i.e expected long-term reward) maximized by the DMN to
correspond to negative surprise,
that is, the log-likehood of current sensory priors
the agent has about the world. More explicitly, this corresponds to using free-energy as a Q-value approximator for the MDP, i.e

>>>>

\begin{figure}[!h]
  \includegraphics[width=1\linewidth]{VennDiagram-2017-09-08.pdf}
  \caption{\textbf{Situating Markov Decision Processes among other accounts of default mode function}
  This Venn diagram summarizes the relationship between four existing explanations of the functional role of the DMN and our present account. Viewing empirical findings in the DMN from the MDP viewpoint incorporates important aspects of the free energy principle, predictive coding, sentinal hypothesis, and semantic hypothesis.
  The MDP account may reconcile several strengths of these functional accounts in a process model that simultaneously acknowledges environmental input and behavioral choices as well as the computational and algorithmic properties (How? and What?) underlying higher-order control of the organism.}
  \label{fig:VennDiagram}
\end{figure}

@@

% CRITICISM
% \paragraph{Main criticisms.}
Despite its popularity, criticism against the FEP has arisen over the years,
some of which is outlined in the following.
The main algorithm for minimizing free energy $F_G^R(\x)$ is the \textit{wake-sleep algorithm}
\citep{dayan1995helmholtz}. As these P. Dayan and G. Hinton  noted,
a crucial drawback of the wake-sleep algorithm (and therefore of theories like the FEP \citep{friston2010free} based on it) is that it involves a pair
of forward (generation) and backward (recognition) models $p_G$ and $p_R$ respectively that
together do not correspond to optimization of (a bound of) the marginal likelihood,
because KL divergence is not symmetric in its arguments.
The brain may therefore be unlikely to implement a variant of the wake-sleep algorithm.
The recent theory of
\textit{variational auto-encoders} (VAEs) \citep{kingma2013auto} might provide an efficient alternative to the wake-sleep algorithm. VAEs
overcome a number of the technical limits of the wake-sleep algorithm
by using a reparametrization maneuver, which makes it possible to do differential calculus on random sampling procedures without exploding variance. As a result, unlike the wake-sleep algorithm
for minimizing free energy, VAEs can be efficiently trained via back-propagation of prediction errors.

@@

% \paragraph{Links between FEP and RL.}
We note that FEP and active inference can be reframed in terms of
our model-free RL framework.
This becomes possible by recasting the Q-value function (i.e expected long-term reward) maximized by the DMN to
correspond to negative surprise,
that is, the log-likehood of current sensory priors
the agent has about the world. More explicitly, this corresponds to using free-energy as a Q-value approximator for the MDP, i.e
